---
title: "All state Claims Severity"
output: html_notebook
---



```{r}
set.seed(0) #  setting a seed will ensure reproducible results (not R's seed)
setwd("D:\\uns\\data-valaroziation\\lab\\all_state_claims_insurance")
train = read.csv("allstate_train.csv", header = T)
test = read.csv("allstate_test.csv", header = T)
```

```{r}
library(ggplot2) # Data visualization
library(readr) # CSV file I/O, e.g. the read_csv function
library(corrplot)

```

```{r}
#separate continuous and categorical variables
contVars <- paste0("cont", seq(1, 14))
train_cont <- train[contVars]
train_cont <- cbind(train_cont,train$loss)
catVars <- paste0("cat", seq(1, 116))
train_cat <- train[catVars]
train_cat <- cbind(train_cat,train$loss)
colnames(train_cont)[15] <- "loss"
```

```{r}
#To check missing value in the data set
sum(is.na(train)==TRUE)
```

```{r}
#The total number of categorical variables
cats = grep("cat", colnames(train))
length(cats)
```

```{r}
#number of continous variables
conts = grep("cont", colnames(train))
length(conts)
```

```{r}

```

```{r}
#Digging into Continuous Variables
boxplot(train_cont[,contVars])  #not much outliers
#All continuous variables are within (0,1). They may denote some kind of probabilty
#This shows the dataset is already normalised.
```

```{r}

#correlation matrix for continuous variables
corela = cor(train_cont)
corrplot(corela)   
highCorr <- findCorrelation(corela, cutoff = .75)
```

```{r}




```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
